Star-galaxy Classification Using Deep Convolutional Neural Networks

### 2016-08-10 paper/main.tex
[issue 2.5] luptitudes

To create training images,
we obtain the image FITS files for SDSS fields containing these objects
in five photometric bands: $u$, $g$, $r$, $i$, and $z$.
We use the astrometry information in the FITS headers
in the \texttt{Montage}\footnote{http://montage.ipac.caltech.edu/} software
to align each image to the reference ($r$-band) image.
We then use \texttt{SExtractor} to find the pixel positions of
the 65,000 objects we have selected,
and to center each object in the cutout image.
We also convert the flux values to inverse hyperbolic sine magnitudes
\citep[also known as luptitudes;][]{lupton1999modified}.
Finally, in order to account for the effect of Galactic dust,
extinction corrections in magnitudes are applied
following \cite{schlegel1998maps}.
In the end, we have cutout images of size $48\times48$ pixels
with luptitude values in each pixel.
We note that we have experimented with increasing the pixel dimensions to
$60\times60$ and $72\times72$ pixels, but do not find noticeable
improvement in the performance of our model.

>>>>

To create training images,
we obtain the image FITS files for SDSS fields containing these objects
in five photometric bands: $u$, $g$, $r$, $i$, and $z$.
We use the astrometry information in the FITS headers
in the \texttt{Montage}\footnote{http://montage.ipac.caltech.edu/} software
to align each image to the reference ($r$-band) image.
We then use \texttt{SExtractor} to find the pixel positions of
the 65,000 objects we have selected,
and to center each object in the cutout image.
{
Magnitudes in the SDSS photometric catalog are expressed as inverse hyperbolic
sine magnitudes~\citep[also known as luptitudes;][]{lupton1999modified},
and we follow the SDSS convention and convert all flux values to luptitudes.
}
Finally, in order to account for the effect of Galactic dust,
extinction corrections in magnitudes are applied
following \cite{schlegel1998maps}.
In the end, we have cutout images of size $48\times48$ pixels
with luptitude values in each pixel.
We note that we have experimented with increasing the pixel dimensions to
$60\times60$ and $72\times72$ pixels, but do not find noticeable
improvement in the performance of our model.
